Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex
Added sensor-pi python codes

\section{Results}
\subsection{ALPR Results}
Three data sets were run through each ALPR system. In each case, Intrada ALPR was able to recognize at least twice as many plates as OpenALPR.

@@

>>>>

\section{Results}

\subsection{Image Processing Results}

\subsection{ALPR Results}
Three data sets were run through each ALPR system. In each case, Intrada ALPR was able to recognize at least twice as many plates as OpenALPR.

@@

\subsection*{Image Acquisition}
\begin{spacing}{1}
\begin{lstlisting}[language=python]
#!/usr/bin/env python

from time import sleep
import os
import RPi.GPIO as GPIO
import subprocess
import datetime

GPIO.setmode(GPIO.BCM)
GPIO.setup(24, GPIO.IN)

count = 0
up = False
down = False
command = ""
filename = ""
index = 0
camera_pause = "500"

def takepic(imageName):
  print("picture")
  command = "sudo raspistill -o " + imageName + " -q 100 -t " + camera_pause
  print(command)
  os.system(command)

while(True):
  if(up==True):
    if(GPIO.input(24)==False):
      now = datetime.datetime.now()
      timeString = now.strftime("%Y-%m-%d_%H:%M:%S")
      filename = "photo-"+timeString+".jpg"
      takepic(filename)
      subprocess.call(['./processImage.sh'])
  up = GPIO.input(24)
  count = count+1
  sleep(.1)
print "done"

\end{lstlisting}
\end{spacing}

\subsection*{Image Processing}
\begin{spacing}{1}
\begin{lstlisting}[language=python]

import sys;
from cv import *;
import getopt;

# Resizes the image
def resizeImage(rootdir, filename, prefixString, resizeFactor):

    # Loads the original image
    original_img = LoadImage(rootdir + filename)

    # Creates a destination image
    img = CreateImage(GetSize(original_img), 8, 1)

    # Convert the image to gray_scale
    CvtColor(original_img, img, CV_RGB2GRAY);
    size = GetSize(img)

    # Set up the resized image size
    newImage = CreateImage(( size[0] / resizeFactor, size[1] / resizeFactor), img.depth, img.nChannels)

    # Resize the image
    Resize(img, newImage)
    size = GetSize(newImage)

    # Crop the image
    newImage = newImage[size[1]/3:4*(size[1]/5), 0:]

    # Write the image to files
    SaveImage(prefixString + filename, newImage)

# Gets the appropriate command line arguments
def getCommandLineArguments():
    filename = ""
    prefixString = ""
    try:
        opts, args = getopt.getopt(sys.argv[1:], "n:p:", ["name=", "prefix="])
    except getopt.GetoptError:
        sys.exit(1)
    for opt, arg in opts:
        if opt in ("-n", "-name"):
            filename = arg
        elif opt in ("-p", "-prefix"):
            prefixString = arg

    return filename, prefixString

rootDirectory = ""
resizeFactor = 3

filename, prefixString = getCommandLineArguments()

resizeImage(rootDirectory, filename, prefixString, resizeFactor)
\end{lstlisting}
\end{spacing}

\subsection*{Image Sending}
\begin{spacing}{1}
\begin{lstlisting}[language=python]
# Python script for the pi to post to website after getting an image

import sys
import requests

# This file will post an image to the ACMx server. It uses the 'requests'
# module for Multipart-Encoding of the image file. See 
# http://docs.python-requests.org/ for documentation. Prints server response
# to the console.
# 
# Args:
#		sensorID: The ID of the sensor who recorded the image.
#		image: A file handle that was opened for binary reading.
#					e.g. f = open('img.png', 'rb')
#
#	Returns:
#		(nothing)
#
imagePath = sys.argv[1]
sensorID = 2

print imagePath

image = open(imagePath, 'rb')

url = "http://wsn:raspberryp1@acmxlabs.org/smartlots/pidata"

# Construct the file payload.
fPayload = {"image": image}

# Construct normal form variables payload.
dPayload = {
	"id": sensorID
}
# Create a requests object to handle all the urllib2 stuff.
r = requests.post(url, data=dPayload, files=fPayload)

# Print out the server's response.
print r.text
\end{lstlisting}
\end{spacing}
